Clustering in a hyperbolic model of complex networks.

### 2020-12-11 clustering_infinite_model.tex
Processed referee comments

    \draw node[fill,black!60!green, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uuu,\vvv) {};
    \path (p2)+(0.25,-0.2) node {\color{black!60!green}$p_2$};

@@

	%Right boundary
	\pgfmathsetmacro{\rightbounduuuvvv}{\uuu+exp((\vvv)/2)}
	\draw[domain=\rightbounduuuvvv:\r,smooth,variable=\x,black!60!green,line width=1pt] plot (\x, {2*ln(\x-\uuu)-\vvv});
    %Left boundary
    \pgfmathsetmacro{\leftbounduuuvvv}{\uuu-exp((\vvv)/2)}
    \draw[domain=\leftbounduuuvvv:-\r,smooth,variable=\x,black!60!green,line width=1pt] plot (\x, {2*ln(\uuu-\x)-\vvv});

@@

    \draw node[fill,black!60!green, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uuu,\vvv) {};
    \path (p2)+(-0.2,0.2) node {\color{black!60!green}$p_2$};

>>>>

    \draw node[fill,black!20!green, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uuu,\vvv) {};
    \path (p2)+(0.25,-0.2) node {\color{black!20!green}$p_2$};

@@

	%Right boundary
	\pgfmathsetmacro{\rightbounduuuvvv}{\uuu+exp((\vvv)/2)}
	\draw[domain=\rightbounduuuvvv:\r,smooth,variable=\x,black!20!green,line width=1pt] plot (\x, {2*ln(\x-\uuu)-\vvv});
    %Left boundary
    \pgfmathsetmacro{\leftbounduuuvvv}{\uuu-exp((\vvv)/2)}
    \draw[domain=\leftbounduuuvvv:-\r,smooth,variable=\x,black!20!green,line width=1pt] plot (\x, {2*ln(\uuu-\x)-\vvv});

@@

    \draw node[fill,black!20!green, circle, inner sep=0pt, minimum size=5pt] (p2) at (\uuu,\vvv) {};
    \path (p2)+(-0.2,0.2) node {\color{black!20!green}$p_2$};

### 2020-12-11 hyperbolic_degrees.tex
Processed referee comments

\begin{proof}
Recall that when $y^\prime \ge R - y$ then $p^\prime \in \BallHyp{y}$ while for $y^\prime < R - y$ this is true when~\eqref{eq:def_Omega_hyperbolic} holds. We does split the integral for $\mu_{Po,n}(y)$ accordingly, into two integrals $I_1$ and $I_2$,
\begin{align*}
\mu_{\Po}(y) 
&= \int_0^{R-y} 2\Phi(y,y_1)\frac{\alpha\nu}{\pi}e^{-\alpha y_1} dy_1+\int_{R-y}^R \frac{\pi n}{\nu} \frac{\alpha \nu}{\pi}e^{-\alpha y_1}dy_1 =: I_1+I_2.
\end{align*}
Firstly, we will show that the second integral $I_2=o(\mu(y))$ and then we will show that $I_1 = (1+o(1))\mu(y)$ (both with  convergence uniform in $0\leq y\leq (1-\epsilon)R$).

@@

\begin{proof}
We will show that
\[
	\int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{\Po}(y)) = k_n} \alpha e^{-\alpha y} \dd y
	= (1+o(1))\int_0^\infty \Pee(\Po(\xi e^{\frac{z}{2}})=k_n) \alpha e^{-\alpha z} \dd z.
\]
This implies the result because the last integral equals $(1+o(1))2\alpha \xi^{2\alpha} k_n^{-(2\alpha+1)} = (1+o(1))\pmf(k_n)$.

@@

Let us now define the \emph{stripe}
\begin{equation}\label{eq:def_stripe}
	\stripknc = \Rcal \cap (\R_+ \times \Kcal_C(k_n)).
\end{equation} 
and in addition define, for any $0 < \varepsilon < 1$, the following set
\begin{equation}\label{eq:def_joint_degree_set_E_growing_k}
	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \stripknc
		\, : \,  |x - x^\prime|_n > k_n^{1 + \varepsilon} \right\}, 
\end{equation}
where $|x|_n = \min\{|x|, \pi e^{R/2} - |x|\}$ denotes the norm on the finite box $\Rcal$ where the left and right boundaries are identified. Then for any two points $p,p^\prime \in \mathcal{E}_\varepsilon(k_n)$ the expect number of joint neighbours is $\smallO{k_n}$.

@@

We now proof the result for the factorial moments.

@@

Recall that, for any $0 < \varepsilon < 1$
\begin{align*}
	\Prob{D_{\Po} = k_n + t} &= \int_0^R \Prob{\Po(\mu_{Po,n}(y)) = k_n+ t} \alpha e^{-\alpha y} dy\\
	&= \int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po,n}(y)) = k_n+ t} \alpha e^{-\alpha y} dy \\
	&\hspace{10pt}+ \int_{(1-\varepsilon)R}^R \Prob{\Po(\mu_{Po,n}(y)) = k_n+ t} \alpha e^{-\alpha y} dy
\end{align*}
By Lemma~\ref{lem:degree_integral} the first part is $(1+o(1)) \pmf(k_n + t)$ while the second part is $O(n^{-2\alpha(1-\varepsilon)})$ and hence
\[
	\Prob{D_{\Po} = k_n + t} \le \bigO{1}\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right).
\]
In addition we have that $\Prob{Z(n,t) = t} \le \bigO{1} \frac{\Exp{Z(n,t)}}{t}$. We thus obtain
\begin{align*}
	\sum_{t = 1}^{N-n} \Prob{Z(n,t) = t}\Prob{D_{\Po} = k_n + t}
	&\le \bigO{1} \sum_{t = 1}^{N-n} \frac{\Exp{Z(n,t)}}{t}\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)\\
	&= \bigO{1} \sum_{t = 1}^{N-n} \frac{(N-m)(k_n + t)}{N}\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)\\
	&= \bigO{\sqrt{\frac{\log n}{n}}} \sum_{t = 1}^{N-n} \frac{k_n}{t}
		\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)\\
	&\hspace{10pt}+ \bigO{\sqrt{\frac{\log n}{n}}} \sum_{t = 1}^{N-n}
		\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right),
\end{align*}
where we used that $\frac{N-n}{N} = \bigO{\sqrt{\frac{\log n}{n}}}$.

@@

If $k_n=(1+o(1))c n^{\frac{1}{2\alpha+1}}$, then by Lemma~\ref{lem:expnnkn},
\begin{align*}
	\Exp{N_{Po}(k_n)} &= (1+o(1))2\alpha \xi^{2\alpha} n (1+o(1))^{-(2\alpha+1)} c^{-(2\alpha+1)}n^{-1} \\
	&= (1+o(1))2\alpha \xi^{2\alpha} c^{-(2\alpha+1)}=(1+o(1))\zeta,
\end{align*}
which implies $\Exp{N_{Po}(k_n)} \rightarrow \zeta$ (as $\zeta$ is a positive constant). From Lemma~\ref{lem:factmoment}, it then follows that $\Exp{{N_{Po}(k_n) \choose r}} =(1+o(1))\frac{(\Exp{ N_{Po}(k_n)})^r}{r!}\rightarrow \frac{\zeta^r}{r!}$. Thus, it follows from \cite[Theorem 8.3.1]{alon2016probabilistic} that $N_{Po}(k_n) \xrightarrow{d} Po(\zeta)$ for the Poissonized version.

>>>>

\begin{proof}
Recall that when $y^\prime \ge R - y$ then $p^\prime \in \BallHyp{y}$ while for $y^\prime < R - y$ this is true when~\eqref{eq:def_Omega_hyperbolic} holds. We split the integral for $\mu_{Po,n}(y)$ accordingly, into two integrals $I_1$ and $I_2$,
\begin{align*}
\mu_{\Po}(y) 
&= \int_0^{R-y} 2\Phi(y,y_1)\frac{\alpha\nu}{\pi}e^{-\alpha y_1} dy_1+\int_{R-y}^R \frac{\pi n}{\nu} \frac{\alpha \nu}{\pi}e^{-\alpha y_1}dy_1 =: I_1+I_2.
\end{align*}
Firstly, we will show that the second integral $I_2=o(\mu(y))$ and then we will show that $I_1 = (1+o(1))\mu(y)$ (both with  convergence uniform in $0\leq y\leq (1-\epsilon)R$).

@@

\begin{proof}
We will show that
\[
	\int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{\Po}(y)) = k_n} \alpha e^{-\alpha y} \dd y
	= (1+o(1))\int_0^\infty \Pee(\Po(\xi e^{\frac{z}{2}})=k_n) \alpha e^{-\alpha z} \dd z.
\]
This implies the result because the last integral equals $(1+o(1))2\alpha \xi^{2\alpha} k_n^{-(2\alpha+1)} = (1+o(1))\pmf(k_n)$. Where the last asymptotic equality follows from~\eqref{eq:degree_distribution_P_asymptotics}.

@@

Let us now define the \emph{stripe}
\begin{equation}\label{eq:def_stripe}
	\stripknc = \Rcal \cap (\R_+ \times \Kcal_C(k_n)).
\end{equation} 
and in addition define, for any $0 < \varepsilon < 1$, the following set
\begin{equation}\label{eq:def_joint_degree_set_E_growing_k}
	\mathcal{E}_{\varepsilon}(k_n) = \left\{(p,p^\prime) \in \stripknc
		\, : \,  |x - x^\prime|_n > k_n^{1 + \varepsilon} \right\}, 
\end{equation}
where $|x|_n = \min\{|x|, \pi e^{R/2} - |x|\}$ denotes the norm on the finite box $\Rcal$ where the left and right boundaries are identified. Then for any two points $p,p^\prime \in \mathcal{E}_\varepsilon(k_n)$ the expected number of joint neighbours is $\smallO{k_n}$.

@@

We now prove the result for the factorial moments.

@@

Recall that, for any $0 < \varepsilon < 1$
\begin{align*}
	\Prob{D_{\Po} = k_n + t} &= \int_0^R \Prob{\Po(\mu_{Po,n}(y)) = k_n+ t} \alpha e^{-\alpha y} dy\\
	&= \int_0^{(1-\varepsilon)R} \Prob{\Po(\mu_{Po,n}(y)) = k_n+ t} \alpha e^{-\alpha y} dy \\
	&\hspace{10pt}+ \int_{(1-\varepsilon)R}^R \Prob{\Po(\mu_{Po,n}(y)) = k_n+ t} \alpha e^{-\alpha y} dy
\end{align*}
By Lemma~\ref{lem:degree_integral} the first part is $(1+o(1)) \pmf(k_n + t)$ while the second part is $O(n^{-2\alpha(1-\varepsilon)})$ and hence
\[
	\Prob{D_{\Po} = k_n + t} \le \bigO{1}\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right).
\]
In addition we have that $\Prob{Z(n,t) = t} \le \bigO{1} \frac{\Exp{Z(n,t)}}{t}$. We thus obtain
\begin{align*}
	\sum_{t = 1}^{N-n} \Prob{Z(n,t) = t}\Prob{D_{\Po} = k_n + t}
	&\le \bigO{1} \sum_{t = 1}^{N-n} \frac{\Exp{Z(n,t)}}{t}\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)\\
	&= \bigO{1} \sum_{t = 1}^{N-n} \frac{(N-n)(k_n + t)}{N}\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)\\
	&= \bigO{\sqrt{\frac{\log n}{n}}} \sum_{t = 1}^{N-n} \frac{k_n}{t}
		\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right)\\
	&\hspace{10pt}+ \bigO{\sqrt{\frac{\log n}{n}}} \sum_{t = 1}^{N-n}
		\left(\pmf(k_n + t) + n^{-2\alpha(1-\varepsilon)}\right),
\end{align*}
where we used that $\frac{N-n}{N} = \bigO{\sqrt{\frac{\log n}{n}}}$.

@@

If $k_n=(1+o(1))c n^{\frac{1}{2\alpha+1}}$, for some positive constant $c > 0$. then by Lemma~\ref{lem:expnnkn},
\begin{align*}
	\Exp{N_{Po}(k_n)} &= (1+o(1))2\alpha \xi^{2\alpha} n (1+o(1))^{-(2\alpha+1)} c^{-(2\alpha+1)}n^{-1} \\
	&= (1+o(1))2\alpha \xi^{2\alpha} c^{-(2\alpha+1)}=(1+o(1))\zeta,
\end{align*}
which implies $\Exp{N_{Po}(k_n)} \rightarrow \zeta$ (as $\zeta$ is a positive constant). From Lemma~\ref{lem:factmoment}, it then follows that $\Exp{{N_{Po}(k_n) \choose r}} =(1+o(1))\frac{(\Exp{ N_{Po}(k_n)})^r}{r!}\rightarrow \frac{\zeta^r}{r!}$. Thus, it follows from \cite[Theorem 8.3.1]{alon2016probabilistic} that $N_{Po}(k_n) \xrightarrow{d} Po(\zeta)$ for the Poissonized version.

### 2020-12-11 paper.tex
Processed referee comments

\paragraph{Acknowledgments} We are grateful to Dmitri Krioukov for pointing us to the problem of local clustering in this model 
and his helpful insights during discussions of the topic. We are grateful to Remco van der Hofstad for pointing out a mistake in an earlier version of the proof of Theorem~\ref{thm:mainktoinfty}.

>>>>

\paragraph{Acknowledgments} We are grateful to Dmitri Krioukov for pointing us to the problem of local clustering in this model and his helpful insights during discussions of the topic. We thank Remco van der Hofstad for pointing out a mistake in an earlier version of the proof of Theorem~\ref{thm:mainktoinfty}. We also thank an anonymous referee for his/her suggestions and comments on improving the manuscript.
